The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-10-12 talk/vmil2012/presentation/talk.tex
typo
add figures for guard compilation
some low-level notes

\begin{frame}
  \frametitle{Symbolic Frame Capturing}
  \begin{itemize}
      \item Guard can fail deep inside inlined function
      \item when going back to the interpreter, call stack needs to be re-created
      \item done with the help of symbolic frame stacks
      \item these show how trace trace variables fill the to-be-built stack frames
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Interaction with Optimization}
  \begin{itemize}
      \item Some optimizations make it necessary to store extra information in symbolic frames
      \item examples:
          \begin{itemize}
              \item delayed heap stores (need to do stores before resuming interpreter)
              \item allocation remvoal (need to allocate objects before resuming)
          \end{itemize}
      \item can be compressed using similar techniques
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Emitting Guards}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Symbolic Frame Capturing}
  \begin{itemize}
      \item Guard can fail deep inside inlined function
      \item when going back to the interpreter, call stack needs to be re-created
      \item done with the help of symbolic frame stacks
      \item these show how trace variables fill the to-be-built stack frames
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Interaction with Optimization}
  \begin{itemize}
      \item Some optimizations make it necessary to store extra information in symbolic frames
      \item examples:
          \begin{itemize}
              \item delayed heap stores (need to do stores before resuming interpreter)
              \item allocation removal (need to allocate objects before resuming)
          \end{itemize}
      \item can be compressed using similar techniques
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Emitting Guards}
  Guards are compiled as
  \begin{itemize}
    \item Quick Check if the condition holds
    \item and a mapping of machine locations to JIT-variables % indirection using the fail-boxes
  \end{itemize}
  In case of failure
  \begin{itemize}
    \item execution jumps to compensation code, decodes and stores mapping
    \item returns to interpreter that rebuilds state
  \end{itemize}
\end{frame}

\begin{frame}
  \begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{figures/loop.pdf}
  \label{fig:trampoline}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{figures/bridge_compiled.pdf}
  \label{fig:trampoline}
  \end{figure}
\end{frame}
\begin{frame}
  \begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{figures/bridge_patched.pdf}
  \label{fig:trampoline}
  \end{figure}
\end{frame}
